A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-03-23 2022/Sensors/sensors.tex
fix one more mistake

The degree of proximity of a test object to one of the known objects can be expressed in terms of the distance
\begin{equation}
d_i^l = |x_i^l - x^{*l}|
\end{equation} 
on the $l$-th scale.

Thus, the distance $d(\omega_i,\omega_j)$ between two objects $\omega_i$ and $\omega_j$ on a one-dimensional scale will correspond to the minimum distance among all the mappings. If we find the minimum distance among all these distances, we get the nearest neighbour
\begin{equation}
d_{min} = \min \{ d_i^l \} = \min \{ |x_i^l - x^{*l}| \}.
\end{equation}

@@

\begin{itemize}
\item For each scale, search for the closest object to $\omega^*$; the result is a set of distances between the test object and the closest object for each scale.
\item The object with minimal distance on all scales is selected.
\item This object is saved in a special vector and excluded from the set of objects.
\item The whole procedure is repeated $K$ times, resulting in a vector of K nearest neighbours.
\item The number of objects belonging to each class is counted and the decision is made whether   the test object belongs to a particular class.
\item If re-classification is required, the procedure is called to recover the previously excluded objects and search for neighbours.
\end{itemize}

>>>>

The degree of proximity of a test object $\omega^*$ to one of the known objects $\omega_i$ can be expressed in terms of the distance
\begin{equation}
d_i^l = |x_i^l - x^{*l}|
\end{equation} 
on the $l$-th scale.

Thus, the distance $d(\omega_i,\omega^*)$ between two objects $\omega_i$ and $\omega^*$ on a one-dimensional scale will correspond to the minimum distance among all the mappings 
\[
d(\omega_i,\omega^*) = \min_{0\leq l\leq L} d_i^l = \min_{0\leq l\leq L}  |x_i^l - x^{*l}| .
\]
If we find the minimum distance
\begin{equation}
d_{min} = \min_{1\leq i\leq n} d(\omega_i,\omega^*) ,
\end{equation} 
we get the nearest neighbour.

@@

\begin{itemize}
\item For each scale, search for the closest object to $\omega^*$; the result is a set of distances between the test object and the closest object for each scale.
\item The object with minimal distance on all scales is selected.
\item This object is saved in a special vector and excluded from the set of objects.
\item The whole procedure is repeated $K$ times, resulting in a vector of $K$ nearest neighbours.
\item The number of objects belonging to each class is counted and the decision is made whether   the test object belongs to a particular class.
\item If re-classification is required, the procedure is called to recover the previously excluded objects and search for neighbours.
\end{itemize}
